\problemname{Bela}

Young Mirko is a smart, but mischievous boy who often wanders around
parks looking for new ideas.  This time he's come across pensioners
playing the card game Belote. They've invited him to help them
determine the total number of points in a game.

Each card can be uniquely determined by its number and suit. A set of
four cards is called a hand. At the beginning of a game one suit that
``trumps'' any other is chosen, and it is called the dominant
suit. The number of points in a game is equal to the sum of values of
each card from each hand in the game. Mirko has noticed that the
pensioners have played $N$ hands and that suit $B$ was the dominant
suit.

The value of each card depends on its number and whether its suit is
dominant, and is given in Table~\ref{tab:score}.

\begin{table}[h]
  \centering
  \begin{tabular}{ccc}
    Number & \multicolumn{2}{c}{Value}\\
& Dominant & Not dominant\\
\texttt{A} & $11$ & $11$\\
\texttt{K} & $4$ & $4$\\
\texttt{Q} & $3$ & $3$\\
\texttt{J} & $20$ & $2$\\
\texttt{T} & $10$ & $10$\\
\texttt{9} & $14$ & $0$\\
\texttt{8} & $0$ & $0$\\
\texttt{7} & $0$ & $0$\\
  \end{tabular}
  \caption{Scores}
  \label{tab:score}
\end{table}

Write a programme that will determine and output the number of points in the game.

\section*{Input}

The first line contains the number of hands $N$ ($1 \leq N \leq 100$) and the value of suit $B$ (\texttt{S}, \texttt{H}, \texttt{D}, \texttt{C})
from the task.
Each of the following $4N$ lines contains the description of a card (the first character is the number
of the $i$-th card (\texttt{A}, \texttt{K}, \texttt{Q}, \texttt{J}, \texttt{T}, \texttt{9}, \texttt{8}, \texttt{7}), and the second is the suit (\texttt{S}, \texttt{H}, \texttt{D}, \texttt{C})).

\section*{Output}

The first and only line of output must contain the number of points from the task.